Explore gene filtering strategy

### 2025-07-14 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/filter-genes.Rmd

* Endothelial --> Endo
* Fibroblasts --> Fibro
* Neuroendocrine --> NE

```{r}
singler_long_df <- singler_long_df |>
  # shorten labels
  dplyr::mutate(
    short_label = dplyr::case_when(
      singler_label == "Endothelial" ~ "Endo",
      singler_label == "Fibroblast" ~ "Fibro",
      singler_label == "Neuroendocrine" ~ "NE",
      .default = singler_label
    )
  )

>>>>

* Endothelial --> Endo
* Fibroblasts --> Fibro
* Neuroendocrine --> NE
* Stromal other --> stromal

```{r}
singler_long_df <- singler_long_df |>
  # shorten labels
  dplyr::mutate(
    short_label = dplyr::case_when(
      singler_label == "Endothelial" ~ "Endo",
      singler_label == "Fibroblast" ~ "Fibro",
      singler_label == "Neuroendocrine" ~ "NE",
      singler_label == "Stromal other" ~ "stromal",
      .default = singler_label
    )
  )
